manuscript_figures

### 2024-05-24 scripts/manuscript_figures.Rmd
making figure 2

>>>>

```
# Make Figure 2

```{r}

# Aggregate the data by year, site, and transect and compute mean values
aggregated_data <- merged.dat %>%
  group_by(year, site, transect) %>%
  summarize(mean_fish_biomass = mean(Fish.Biomass..g.m2., na.rm = TRUE),
            mean_kelp_cover = mean(COVER, na.rm = TRUE)) %>%
  ungroup()

# Perform linear regression
lm_model <- lm(mean_fish_biomass ~ mean_kelp_cover, data = aggregated_data)
lm_summary <- tidy(lm_model)

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  geom_text(data = lm_summary, aes(label = paste("R² =", round(r.squared, 2), ", p =", signif(p.value, 2))),
            x = Inf, y = Inf, hjust = 1, vjust = 1, size = 4, parse = TRUE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_minimal();figure.2
